Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change

### 2024-12-18 ms.qmd
Fixed tree issue. Was just using wrong tree object

# Check and prune tree
tree_lnrr_wild <- tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good

>>>>

# Check and prune tree
tree_lnrr_wild <- tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_lnrr_wild, dataCol = "species_full", type = "check") # Good
